Mixture Models for Single-Cell Assays with Application to Vaccine Studies

### 2013-05-15 MIMOSA.tex
Update Figure 4

\begin{figure}
\centering
\includegraphics{TIKZFig4.eps}
%\begin{tikzpicture} [auto, node distance=0 cm]
%\node at (0,0) (A) {
%\begin{tikzpicture}
%\node[anchor=south west, inner sep=0] at (0,0) (foo) {\includegraphics[width=0.45\columnwidth]{Figures/Fluidigm_Multivariate_BIRC3_CCL5_Unstim_Counts.pdf}};
%\begin{scope} [x={(foo.south east)},y={(foo.north west)}]
%\node at (0,1) [font=\small\sffamily] {A} ;
%\end{scope}
%\end{tikzpicture}
%};
%\node [right=of A] (B){
%\begin{tikzpicture}
%\node[anchor=south west, inner sep=0] at (0,0) (bar) {\includegraphics[width=0.45\columnwidth]{Figures/Fluidigm_Multivariate_BIRC3_CCL5_Stim_Counts.pdf}};
%\begin{scope} [x={(bar.south east)},y={(bar.north west)}]
%\node at (-0.02,1) [font=\small\sffamily] {B} ;
%\end{scope}
%\end{tikzpicture}
%};
%%\node [anchor = south west, inner sep=0] at (0,-4) {\includegraphics[width=0.4\columnwidth]{Fluidigm_Multivariate_Marginalized_BIRC3_CCL5.pdf}};
%%\node [anchor=south west, inner sep=0] at (6.5,-4) {\includegraphics[width=0.4\columnwidth]{Fluidigm_Multivariate_BIRC3_CCL5.pdf}};
%%\node at (0,0) [font=\small\sffamily] {C} ;
%%\node at (6.25,0) [font=\small\sffamily] {D} ;
%\end{tikzpicture}
\caption{Counts of cells expressing different combinations of BIRC3 and CCL5 genes in the A) unstimulated and B) stimulated conditions. No difference is observed from the marginalized counts, while multivariate MIMOSA detects a difference between stimulated and unstimulated conditions in 13 of 16 samples. Sample names highlighted in red identify those where MIMOSA did not detect a difference. This figure appears in color in the electronic version of this article.}
\label{fig:polyfunctionality}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics{TIKZFig4.eps}
%\begin{tikzpicture} [auto, node distance=0 cm]
%\node at (0,0) (A) {
%\begin{tikzpicture}
%\node[anchor=south west, inner sep=0] at (0,0) (foo) {\includegraphics[width=0.45\columnwidth]{Figures/Fluidigm_Multivariate_BIRC3_CCL5_Unstim_Counts.pdf}};
%\begin{scope} [x={(foo.south east)},y={(foo.north west)}]
%\node at (0,1) [font=\small\sffamily] {A} ;
%\end{scope}
%\end{tikzpicture}
%};
%\node [right=of A] (B){
%\begin{tikzpicture}
%\node[anchor=south west, inner sep=0] at (0,0) (bar) {\includegraphics[width=0.45\columnwidth]{Figures/Fluidigm_Multivariate_BIRC3_CCL5_Stim_Counts.pdf}};
%\begin{scope} [x={(bar.south east)},y={(bar.north west)}]
%\node at (-0.02,1) [font=\small\sffamily] {B} ;
%\end{scope}
%\end{tikzpicture}
%};
%%\node [anchor = south west, inner sep=0] at (0,-4) {\includegraphics[width=0.4\columnwidth]{Fluidigm_Multivariate_Marginalized_BIRC3_CCL5.pdf}};
%%\node [anchor=south west, inner sep=0] at (6.5,-4) {\includegraphics[width=0.4\columnwidth]{Fluidigm_Multivariate_BIRC3_CCL5.pdf}};
%%\node at (0,0) [font=\small\sffamily] {C} ;
%%\node at (6.25,0) [font=\small\sffamily] {D} ;
%\end{tikzpicture}
\caption{Counts of cells expressing A) different combinations of CCR7 and GZMK genes in the unstimulated and stimulated conditions (+/+,+/-,-/+,-/-), and for B) the marginalized positive counts in stimulated and unstimulated conditions. No difference is observed from the marginalized counts, while multivariate MIMOSA detects a difference between stimulated and unstimulated conditions in 12 of 16 samples, while Fisher's test detects 9 of 16. Sample names highlighted in red identify those where MIMOSA did not detect a difference. This figure appears in color in the electronic version of this article.}
\label{fig:polyfunctionality}
\end{figure}

### 2013-05-15 TIKZFig4.tex
Update Figure 4

\documentclass{article}
\usepackage{tikz,amsmath,siunitx}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows,snakes,backgrounds,patterns,matrix,shapes,fit,calc,shadows,plotmarks}
\usepackage[graphics,tightpage,active]{preview}
\PreviewEnvironment{tikzpicture}
\PreviewEnvironment{equation}
\PreviewEnvironment{equation*}
\newlength{\imagewidth}
\newlength{\imagescale}
\pagestyle{empty}
\thispagestyle{empty}
\begin{document}
\begin{tikzpicture} [auto, node distance=0 cm]
\node at (0,0) (A) {
\begin{tikzpicture}
\node[anchor=south west, inner sep=0] at (0,0) (foo) {\includegraphics[width=0.5\columnwidth]{Figures/Fluidigm_Multivariate_BIRC3_CCL5_Unstim_Counts.pdf}};
\begin{scope} [x={(foo.south east)},y={(foo.north west)}]
\node at (0,1) [font=\tiny\sffamily] {A} ;
\end{scope}
\end{tikzpicture}
};
\node [right=of A] (B){
\begin{tikzpicture}
\node[anchor=south west, inner sep=0] at (0,0) (bar) {\includegraphics[width=0.5\columnwidth]{Figures/Fluidigm_Multivariate_BIRC3_CCL5_Stim_Counts.pdf}};
\begin{scope} [x={(bar.south east)},y={(bar.north west)}]
\node at (-0.02,1) [font=\tiny\sffamily] {B} ;
\end{scope}
\end{tikzpicture}
};
%\node [anchor = south west, inner sep=0] at (0,-4) {\includegraphics[width=0.4\columnwidth]{Fluidigm_Multivariate_Marginalized_BIRC3_CCL5.pdf}};
%\node [anchor=south west, inner sep=0] at (6.5,-4) {\includegraphics[width=0.4\columnwidth]{Fluidigm_Multivariate_BIRC3_CCL5.pdf}};
%\node at (0,0) [font=\small\sffamily] {C} ;
%\node at (6.25,0) [font=\small\sffamily] {D} ;
\end{tikzpicture}\end{document}

>>>>

\documentclass{article}
\usepackage{tikz,amsmath,siunitx}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows,snakes,backgrounds,patterns,matrix,shapes,fit,calc,shadows,plotmarks}
\usepackage[graphics,tightpage,active]{preview}
\PreviewEnvironment{tikzpicture}
\PreviewEnvironment{equation}
\PreviewEnvironment{equation*}
\newlength{\imagewidth}
\newlength{\imagescale}
\pagestyle{empty}
\thispagestyle{empty}
\begin{document}
\begin{tikzpicture} [auto, node distance=0 cm]
\node at (0,0) (A) {
\begin{tikzpicture}
\node[anchor=south west, inner sep=0] at (0,0) (foo) {\includegraphics[width=0.5\columnwidth]{Figures/revised_Fluidigm_Multivariate_CCR7_GZMK.pdf}};
\begin{scope} [x={(foo.south east)},y={(foo.north west)}]
\node at (0,1) [font=\tiny\sffamily] {A} ;
\end{scope}
\end{tikzpicture}
};
\node [right=of A] (B){
\begin{tikzpicture}
\node[anchor=south west, inner sep=0] at (0,0) (bar) {\includegraphics[width=0.5\columnwidth]{Figures/revised_Fluidigm_Marginal_CCR7_GZMK.pdf}};
\begin{scope} [x={(bar.south east)},y={(bar.north west)}]
\node at (-0.02,1) [font=\tiny\sffamily] {B} ;
\end{scope}
\end{tikzpicture}
};
%\node [anchor = south west, inner sep=0] at (0,-4) {\includegraphics[width=0.4\columnwidth]{Fluidigm_Multivariate_Marginalized_BIRC3_CCL5.pdf}};
%\node [anchor=south west, inner sep=0] at (6.5,-4) {\includegraphics[width=0.4\columnwidth]{Fluidigm_Multivariate_BIRC3_CCL5.pdf}};
%\node at (0,0) [font=\small\sffamily] {C} ;
%\node at (6.25,0) [font=\small\sffamily] {D} ;
\end{tikzpicture}\end{document}
